MLH1 data report 

### 2017-10-12 rmd_report.rmd
working on simulation things

```{r first boxplots, echo=FALSE, fig.align='center'}

ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci)) + geom_boxplot(data = MLH1_data, aes(fill = factor(strain) ) ) + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen"))
ff <- ff + facet_wrap(~ sex, scales="free")
ff
```

>>>>

```{r first boxplots, echo=FALSE, fig.align='center'}
ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci)) + geom_boxplot(data = MLH1_data, aes(fill = factor(strain) ) ) + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen"))
ff <- ff + facet_wrap(~ sex, scales="free")
ff
```
